\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{microtype}
\usepackage{titlesec}

\geometry{left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

\titleformat{\section}{\Large\bfseries\color{blue!70!black}}{}{0em}{}[\titlerule]
\setlength{\parskip}{4pt}

% Custom spacing variable
\newlength{\jobspacing}
\setlength{\jobspacing}{0.8em}

\begin{document}
\raggedright
\sloppy

\begin{center}
    {\LARGE \textbf{Alejandro Gutiérrez Franco}}\\
    \textbf{Roku Developer} \\
    Bogotá, Colombia | +57 320 244 0076 | \href{mailto:alejandrogfster@gmail.com}{alejandrogfster@gmail.com} \\
    \href{https://www.linkedin.com/in/alejandro-gutierrez-franco-06214674}{LinkedIn} |
    \href{https://github.com/fragualej/hello-roku}{GitHub}
\end{center}

\section*{Profile}
I'm a Roku Developer with experience in creating engaging and user-friendly streaming channels for Roku devices. I have expertise in Roku's BrightScript language, SceneGraph framework, and RAF (Roku Ad Framework), SSAI (Server Side Ad Insertion) and CSAI (Client Side Ad Insertion). I am passionate about delivering high-quality content and products that enhance the streaming experience for millions of Roku users worldwide. Beyond coding, I enjoy running, reading, cooking, and exploring the magic of cinema. Always open to networking and discussing the future of OTT!

\section*{Top Skills}
\begin{multicols}{2}
\begin{itemize}
    \item BrightScript \& SceneGraph
    \item Roku Ads: RAF, SSAI \& CSAI
    \item Roku Tools: RALE, Roku Stream Tester
    \item Git, BrighterScript, Rooibos
    \item API REST \& GraphQL
    \item JavaScript, CSS, HTML, React
    \item Communication, Collaboration, Teamwork
\end{itemize}
\end{multicols}

\section*{Experience}

\textbf{Globant - TelevisaUnivision, Remote} \\
\emph{Roku Developer} \hfill \textit{Apr 2024 -- Present} \\
\begin{itemize}[leftmargin=*]
    \item Optimized app performance by removing ghost animations and resolving analytics discrepancies.
    \item Implemented Charles Proxy debugging tools for streamlined development workflows.
    \item Enhanced UI consistency with refined padding, scrub bar adjustments, and visual improvements.
    \item Delivered comprehensive bug fixes to improve overall user experience.
\end{itemize}

\vspace{\jobspacing}

\textbf{X-Team - Venu Sports, Remote} \\
\emph{Roku Developer} \hfill \textit{Oct 2024 -- Feb 2025} \\
\begin{itemize}[leftmargin=*]
    \item Refactored navigation architecture to enhance user flow and reduce friction.
    \item Developed enhanced debug menu functionality for efficient DMA compliance testing.
    \item Implemented data validation systems ensuring accurate analytics reporting.
    \item Resolved critical performance bottlenecks and application stability issues.
\end{itemize}

\vspace{\jobspacing}

\textbf{Stand8 - NBCUniversal, Remote} \\
\emph{Roku Developer} \hfill \textit{Jul 2023 -- Aug 2024} \\
\begin{itemize}[leftmargin=*]
    \item Delivered 2024 Olympics features including dedicated screens, GraphQL bridges, and event integration.
    \item Enhanced accessibility with global text-to-speech component for improved user experience.
    \item Built custom date/time handling functions for legacy device compatibility.
    \item Developed pause ad component integrated within video player UI for seamless ad delivery.
    \item Refactored navigation system eliminating focus glitches and screen transition issues.
    \item Implemented data validation to ensure accurate analytics reporting and system reliability.
\end{itemize}

\vspace{\jobspacing}

\textbf{Globant - PBS Kids | PBS GA, Remote} \\
\emph{Roku Developer} \hfill \textit{Apr 2022 -- Jun 2023} \\
\begin{itemize}[leftmargin=*]
    \item Architected complete video playback system using SGDEX framework with DRM support, ads integration, and optimized performance through SceneGraph threading.
    \item Developed comprehensive HTTP data services for Home and Details screens with robust error handling.
    \item Integrated Roku Ads Framework (RAF) for seamless ad delivery and revenue optimization.
    \item Built StationScreen with donation features, TV Guide functionality, and enhanced accessibility via text-to-speech.
    \item Implemented user-friendly error handling for connectivity, location, and server issues.
\end{itemize}

\vspace{\jobspacing}

\textbf{Globant - Discovery Channel, Remote} \\
\emph{Roku Developer} \hfill \textit{Nov 2021 -- Mar 2024} \\
\begin{itemize}[leftmargin=*]
    \item Contributed to unit testing with BrighterScript and Rooibos.
\end{itemize}

\vspace{\jobspacing}

\textbf{Globant - NFL , Remote} \\
\emph{Roku Developer} \hfill \textit{Jan 2021 -- Oct 2021} \\
\begin{itemize}[leftmargin=*]
    \item Contributed to the transition from a licensing model to an in-house BrightScript/SceneGraph solution for the NFL.
    \item Developed core UI components, including:
    \begin{itemize}[leftmargin=*]
        \item Horizontal navigation bar
        \item Season/week selector button and modal
        \item Game Details Screen for various game states (upcoming, live, replay)
        \item Audio streaming video interface
    \end{itemize}
    \item Successfully resolved bugs to ensure a seamless user experience.
\end{itemize}

\section*{Education}
\textbf{Bachelor in Mechanical Engineering} \\
Universidad Distrital Francisco José de Caldas, Bogotá \hfill \textit{2012 -- 2014} \\
Meritorious Thesis: UI Development (Matlab GUI-Ansys) for welding joints.

\textbf{Mechanical Engineering Technologist} \\
Universidad Distrital Francisco José de Caldas, Bogotá \hfill \textit{2008 -- 2011} \\
Thesis: UI for strength determination of composite materials.

\section*{Courses}
\begin{itemize}[leftmargin=*]
    \item Pair Programming with a Large Language Model, DeepLearning \hfill \textit{Sep 2025}
    \item ChatGPT Prompt Engineering for Developers, DeepLearning \hfill \textit{Sep 2025}
    \item React basics, Coursera \hfill \textit{Apr 2025}
    \item HTML \& CSS in depth, Coursera \hfill \textit{Feb 2025}
    \item Programming with JavaScript, Coursera \hfill \textit{Jan 2025}
    \item Introduction to Front-End Development, Coursera \hfill \textit{Oct 2024}
    \item Arduino, Universidad de los Andes \hfill \textit{May 2014}
    \item Creative Coding 2.0, Domestika \hfill \textit{May 2022}
    \item BrightScript - SceneGraph, Rolat \hfill \textit{Dec 2020}
\end{itemize}

\section*{Languages}
\textbf{English:} B2 - Fluent

\section*{Hobbies}
Sci-Fi reading, Running, Cooking, Traveling, Watching movies, Dining out.

\section*{References}
\textbf{Eng. Juan Carlos Joya} \\
Televisa Univision \\
Email: jcarl30@gmail.com | Tel: (+57) 311 553 6944

\textbf{Eng. Chris Muench} \\
NBCUniversal \\
Email: cdmuench@gmail.com | Tel: (+1) 562 458 3346

\textbf{Acct. Milena Rojas} \\
Primax Colombia SAS \\
Email: anamrojasc3112@gmail.com | Tel: (+57) 312 446 1785

\end{document}