\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{microtype}
\usepackage{titlesec}

\geometry{left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

\titleformat{\section}{\Large\bfseries\color{blue!70!black}}{}{0em}{}[\titlerule]
\setlength{\parskip}{4pt}

% Custom spacing variable
\newlength{\jobspacing}
\setlength{\jobspacing}{0.8em}

\begin{document}
\raggedright
\sloppy

\begin{center}
    {\LARGE \textbf{Ana Milena Rojas Cantor}}\\
    \textbf{Jefe Procurement Operations Center} \\
    Bogotá, Colombia | +57 312 446 1785 | \href{mailto:anamrojasc1231@gmail.com}{anamrojasc1231@gmail.com} \\
    \href{https://www.linkedin.com/in/alejandro-gutierrez-franco-06214674}{LinkedIn}
\end{center}

\section*{Perfil Profesional}
Profesional en Contaduría Pública con especialización en Finanzas y más de 7 años de experiencia en Compras en los sectores de construcción y Oil \& Gas. Con sólida trayectoria en gobernanza de compras, negociación, planificación estratégica y optimización de procesos, impulsando ahorros y eficiencias operativas. Me destaco por mi liderazgo en proyectos regionales, la gestión del cambio y la capacidad de conectar con las necesidades del negocio para generar valor estratégico y financiero.

\section*{Habilidades}
\begin{multicols}{2}
\begin{itemize}
    \item Gobernanza de compras y cumplimiento normativo.
    \item Negociación estratégica y gestión de contratos.
    \item Optimización y digitalización de procesos de compras.
    \item Análisis de costos y generación de eficiencias.
    \item Category Management y estrategias de compras.
    \item Desarrollo y gestión de proveedores (SRM).
    \item Comunicación efectiva y construcción de relaciones con Stakeholders.
\end{itemize}
\end{multicols}

\section*{Experiencia Profesional}

\textbf{Jefe Procurement Operations Center} \hfill \textit{Bogotá, Colombia} \\
\emph{Primax Colombia S.A} \hfill \textit{Jun 2025 - Presente} \\
\begin{itemize}[leftmargin=*]
    \item Optimized app performance by removing ghost animations and resolving analytics discrepancies.
    \item Implemented Charles Proxy debugging tools for streamlined development workflows.
    \item Enhanced UI consistency with refined padding, scrub bar adjustments, and visual improvements.
    \item Delivered comprehensive bug fixes to improve overall user experience.
\end{itemize}

\vspace{\jobspacing}

\textbf{Procurement Specialist} \hfill \textit{Bogotá, Colombia} \\
\emph{Primax Colombia S.A} \hfill \textit{Mar 2023 - May 2025} \\
\begin{itemize}[leftmargin=*]
    \item Construí y apoye la implementación del Procurement Operations Center (POC) para operaciones en Colombia, Perú y Ecuador, asegurando la correcta gobernanza del proceso de compras.
    \item Recopilé y analicé datos para la construcción de las categorías de compra e identificación de oportunidades de ahorro.
    \item Implementé herramientas tecnológicas para automatizar procesos, aumentando la eficiencia y trazabilidad de las adquisiciones.
    \item Lideré la comunicación interna y externa sobre procesos, mejores prácticas de compras y uso de herramientas digitales.
    \item 
\end{itemize}

\vspace{\jobspacing}

\textbf{Procurement Specialist} \hfill \textit{Bogotá, Colombia} \\
\emph{Hilti Colombia S.A.S} \hfill \textit{Nov 2018 - Feb 2023} \\
\begin{itemize}[leftmargin=*]
    \item Lideré negociaciones de las categorías de Facilities, mercadeo, TI , Travel 
    \item Enhanced accessibility with global text-to-speech component for improved user experience.
    \item Built custom date/time handling functions for legacy device compatibility.
    \item Developed pause ad component integrated within video player UI for seamless ad delivery.
    \item Refactored navigation system eliminating focus glitches and screen transition issues.
    \item Implemented data validation to ensure accurate analytics reporting and system reliability.
\end{itemize}

\vspace{\jobspacing}

\textbf{Globant - PBS Kids | PBS GA, Remote} \\
\emph{Roku Developer} \hfill \textit{Apr 2022 -- Jun 2023} \\
\begin{itemize}[leftmargin=*]
    \item Architected complete video playback system using SGDEX framework with DRM support, ads integration, and optimized performance through SceneGraph threading.
    \item Developed comprehensive HTTP data services for Home and Details screens with robust error handling.
    \item Integrated Roku Ads Framework (RAF) for seamless ad delivery and revenue optimization.
    \item Built StationScreen with donation features, TV Guide functionality, and enhanced accessibility via text-to-speech.
    \item Implemented user-friendly error handling for connectivity, location, and server issues.
\end{itemize}

\vspace{\jobspacing}

\textbf{Globant - Discovery Channel, Remote} \\
\emph{Roku Developer} \hfill \textit{Nov 2021 -- Mar 2024} \\
\begin{itemize}[leftmargin=*]
    \item Contributed to unit testing with BrighterScript and Rooibos.
\end{itemize}

\vspace{\jobspacing}

\textbf{Globant - NFL , Remote} \\
\emph{Roku Developer} \hfill \textit{Jan 2021 -- Oct 2021} \\
\begin{itemize}[leftmargin=*]
    \item Contributed to the transition from a licensing model to an in-house BrightScript/SceneGraph solution for the NFL.
    \item Developed core UI components, including:
    \begin{itemize}[leftmargin=*]
        \item Horizontal navigation bar
        \item Season/week selector button and modal
        \item Game Details Screen for various game states (upcoming, live, replay)
        \item Audio streaming video interface
    \end{itemize}
    \item Successfully resolved bugs to ensure a seamless user experience.
\end{itemize}

\section*{Education}
\textbf{Bachelor in Mechanical Engineering} \\
Universidad Distrital Francisco José de Caldas, Bogotá \hfill \textit{2012 -- 2014} \\
Meritorious Thesis: UI Development (Matlab GUI-Ansys) for welding joints.

\textbf{Mechanical Engineering Technologist} \\
Universidad Distrital Francisco José de Caldas, Bogotá \hfill \textit{2008 -- 2011} \\
Thesis: UI for strength determination of composite materials.

\section*{Courses}
\begin{itemize}[leftmargin=*]
    \item Pair Programming with a Large Language Model, DeepLearning \hfill \textit{Sep 2025}
    \item ChatGPT Prompt Engineering for Developers, DeepLearning \hfill \textit{Sep 2025}
    \item React basics, Coursera \hfill \textit{Apr 2025}
    \item HTML \& CSS in depth, Coursera \hfill \textit{Feb 2025}
    \item Programming with JavaScript, Coursera \hfill \textit{Jan 2025}
    \item Introduction to Front-End Development, Coursera \hfill \textit{Oct 2024}
    \item Arduino, Universidad de los Andes \hfill \textit{May 2014}
    \item Creative Coding 2.0, Domestika \hfill \textit{May 2022}
    \item BrightScript - SceneGraph, Rolat \hfill \textit{Dec 2020}
\end{itemize}

\section*{Languages}
\textbf{English:} B2 - Fluent

\section*{Hobbies}
Sci-Fi reading, Running, Cooking, Traveling, Watching movies, Dining out.

\section*{References}
\textbf{Eng. Juan Carlos Joya} \\
Televisa Univision \\
Email: jcarl30@gmail.com | Tel: (+57) 311 553 6944

\textbf{Eng. Chris Muench} \\
NBCUniversal \\
Email: cdmuench@gmail.com | Tel: (+1) 562 458 3346

\textbf{Acct. Milena Rojas} \\
Primax Colombia SAS \\
Email: anamrojasc3112@gmail.com | Tel: (+57) 312 446 1785

\end{document}